An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-07 EconGrowth.Rnw
Began editing introduction text.

Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor. In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output (\textit{y}) as a function of labor (\textit{l}) and capital (\textit{k}) (MISHRA, 2007).

\begin{equation}
  y_\mathrm{C-D} = A(t) k^\alpha l^\beta
\end{equation}

\begin{equation}
  y \equiv Y/Y_\mathrm{0}
\end{equation}

\begin{equation}
  k \equiv K/K_\mathrm{0}
\end{equation}

\begin{equation}
  l \equiv L/L_\mathrm{0}
\end{equation}

@@

\begin{equation}
  \alpha + \beta = 1
\end{equation}

>>>>

Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor. In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output ($y$) as a function of labor ($l$), capital stock ($k$), and a technological progress term ($\mathmr{e}^(t-t_0)$) \citep{Mishra:2007tv}.

\begin{equation} \label{eq:CD}
  y_\mathrm{C-D} = \mathrm{e}^{(t-t_0)} k^\alpha l^\beta,
\end{equation}

\noindent where

\begin{equation} \label{eq:y_def}
  y \equiv Y/Y_\mathrm{0},
\end{equation}

\begin{equation} \label{eq:k_def}
  k \equiv K/K_\mathrm{0},
\end{equation}

\noindent and

\begin{equation} \label{eq:l_def}
  l \equiv L/L_\mathrm{0}; with
\end{equation}

\noindent $Y$ measured by GDP, $K$ measured in currency units, and $L$ measured in workers or work-hours.

@@

\begin{equation} \label{eq:CD_constant_returns_to_scale_constraint}
  \alpha + \beta = 1
\end{equation}
